\documentclass[paper=a4,fontsize=11pt]{scrartcl}%
\usepackage[T1]{fontenc}%
\usepackage[utf8]{inputenc}%
\usepackage{lmodern}%
\usepackage{textcomp}%
\usepackage{lastpage}%
%
\usepackage{mdframed}%
\usepackage[english]{babel}%
\usepackage[protrusion=true,expansion=true]{microtype}%
\usepackage{amsmath}%
\usepackage{amsfonts}%
\usepackage{amsthm}%
\usepackage{graphicx}%
\usepackage[svgnames]{xcolor}%
\usepackage{geometry}%
\usepackage{url}%
\usepackage{sectsty}%
%
\begin{document}%
\normalsize%
\frenchspacing%
\pagestyle{empty}%
\textheight=700px%
\sectionfont{ \usefont{OT1}{phv}{b}{n} \sectionrule{0pt}{0pt}{-5pt}{3pt}}}%
\newlength{\spacebox}%
\settowidth{\spacebox}{8888888888}%
\newcommand{\sepspace}{
                             \vspace*{1em}
}%
\newcommand{\MyName}[1]{
            \Huge \usefont{OT1}{phv}{b}{n} \hfill #1
            \par \normalsize \normalfont
}%
\newcommand{\MySlogan}[1]{
        \large \usefont{OT1}{phv}{m}{n}\hfill \textit{#1}
        \par \normalsize \normalfont
}%
\newcommand{\NewPart}[1]{
                             \section*{\uppercase{#1}}
}%
\newcommand{\PersonalEntry}[2]{
        \noindent\hangindent=2em\hangafter=0 % Indentation
        \parbox{\spacebox}{        % Box to align text
        \textit{#1}}               % Entry name (birth, address, etc.)
        \hspace{1.5em} #2 \par}    % Entry value
 }%
\newcommand{\SkillsEntry}[2]{

        \noindent\hangindent=2em\hangafter=0 % Indentation
        \parbox{\spacebox}{        % Box to align text
        \textit{#1}}			   % Entry name (birth, address, etc.)
        \hspace{1.5em} #2 \par    % Entry value
}%
\newcommand{\EducationEntry}[4]{
        \noindent \textbf{#1} \hfill      % Study
        \colorbox{Black}{%
            \parbox{6em}{%
            \hfill\color{White}#2}} \par  % Duration
        \noindent \textit{#3} \par        % School
        \noindent\hangindent=2em\hangafter=0 \small #4 % Description
        \normalsize \par
 }%
\newcommand{\WorkEntry}[4]{
         % Same as \EducationEntry
        \noindent \textbf{#1} \hfill      % Jobname
        \colorbox{Black}{\color{White}#2} \par  % Duration
        \noindent \textit{#3} \par              % Company
        \noindent\hangindent=2em\hangafter=0 \small #4 % Description
        \normalsize \par
 }%
\newcommand{\PublicationsEntry}[5]{
         % Same as \EducationEntry
        \noindent \textbf{#1} \hfill      % Jobname
        \colorbox{Black}{\color{White}#2} \par  % Duration
        \noindent \textit{#3} \par              % Company
        \noindent\hangindent=2em\hangafter=0 \small #4 \par % Publisher
        \noindent\hangindent=2em\hangafter=0 \small #5 % Description
        \normalsize \par
 }%
\newcommand{\CertificationsEntry}[2]{

         % Same as \EducationEntry
        \noindent \textbf{#1} \hfill      % Jobname
        \noindent \textit{#2} \par              % Company
        \normalsize \par

}%
\MyName{Abhinav Sharma}%
\MySlogan{Curriculum Vitae}%
\sepspace%
\NewPart{Personal details}{}%
\PersonalEntry{Birth}{January 1, 1980}%
\PersonalEntry{Address}{111 First St, New York}%
\PersonalEntry{Phone}{(123) 000{-}0000}%
\NewPart{Education details}{}%
\EducationEntry{MSc. Name of Education}{2010-2012}{Name of University}{Descriptive text goes here. In order to maintain a stylish look, try to fill this description with a few lines of text. Do the same for the other entries in the education section.}%
\sepspace%
\NewPart{Skills}{}%
\SkillsEntry{Human Languages}{English (fluent)}%
\SkillsEntry{}{Portuguese (fluent)}%
\SkillsEntry{Programming Languages}{Clojure}%
\NewPart{Work details}{}%
\WorkEntry{Chief Technology Officer}{August 2018 - Present}{Cyber Indian App Stores}{I am leading a team of 8 in the core engineering wing.}%
\sepspace%
\WorkEntry{Software Engineer - Machine Learning}{August 2016 - July 2017}{Fourtek (IT) Solutions Pvt. Ltd.}{I worked as a co{-}founder of a product targeting the StartUp ecosystem.}%
\sepspace%
\NewPart{Publication details}{}%
\PublicationsEntry{An Analytical Study to Find the Major Factors Behind the Great Smog of Delhi, 2016: Using Fundamental Data Sciences}{Mar 8, 2018}{Springer}{Guided two undergraduates into the art of storytelling through Data and their hard work eventually landed a paper in the Springer publications.}%
\sepspace%
\PublicationsEntry{An Analytical Study to Find the Major Factors Behind the Great Smog of Delhi, 2016: Using Fundamental Data Sciences}{Mar 8, 2018}{Springer}{Guided two undergraduates into the art of storytelling through Data and their hard work eventually landed a paper in the Springer publications.}%
\sepspace%
\PublicationsEntry{An Analytical Study to Find the Major Factors Behind the Great Smog of Delhi, 2016: Using Fundamental Data Sciences}{Mar 8, 2018}{Springer}{Guided two undergraduates into the art of storytelling through Data and their hard work eventually landed a paper in the Springer publications.}%
\sepspace%
\NewPart{Certifications}{}%
\CertificationsEntry{Learning How to Learn}{University of California San Diego}%
\end{document}